\documentclass[11pt,twoside,a4paper]{article}
%NOTE: This report format is 

\newcommand{\reporttitle}{Final Report: {Your title}}
\newcommand{\reportauthorOne}{Nathaniel Liong}
\newcommand{\cidOne}{2400530}
\newcommand{\reportauthorTwo}{Student 2}
\newcommand{\cidTwo}{your id number}
\newcommand{\reporttype}{Coursework}
\bibliographystyle{plain}

% include files that load packages and define macros
\input{includes} % various packages needed for maths etc.
\input{notation} % short-hand notation and macros


%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% front page
\input{titlepage}


%%%%%%%%%%%%%%%%%%%%%%%%%%% table of content
%If a table of content is needed, simply uncomment the following lines
%\tableofcontents
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Main document
\section*{Note}
\emph{The final report should expand upon the initial proposal, including detailed descriptions of the project's development process, architectural design, implementation details, and experimental evaluations, alongside the final outcomes. The report should highlight the project's achievements, innovations, and the impact of the application. The suggested structure is as follows:}

\section{Introduction}
\begin{itemize}
    \item \emph{\textbf{Project Overview:} Briefly reiterate the idea of your mobile application and its target users.}
    \item \emph{\textbf{Motivation and Background:} Provide an enhanced motivation for the project with additional details and new developments that have influenced the project since the initial proposal.}
    \item \emph{\textbf{Objectives:} Clearly state the specific goals of the application and the healthcare challenges it addresses.}
    \item \emph{\textbf{Impact Discussion:} Expand on the potential societal and individual impacts, supplemented by preliminary feedback or observations.}
\end{itemize}

\section{Literature Review}
\begin{itemize}
    \item \emph{Expand on the initial review of similar works. Include a detailed analysis of at least three relevant existing works.}
    \item \emph{Discuss their key features, limitations, and how your application proposes improvements.}
\end{itemize}

\section{System Architecture and Design}
\begin{itemize}
    \item \emph{\textbf{Architecture Overview:} Describe the overall architecture, including both hardware and software components.}
    \item \emph{\textbf{Design Details:} Elaborate on the design choices and their alignment with the project objectives, including the integration of front-end, back-end, and database components.}
    \item \emph{Describe the data flow through the system, particularly how it integrates mobile sensors, communication, and AI.}
\end{itemize}

\section{Implementation and Development}
\begin{itemize}
    \item \emph{Discuss the integration and improvements of mobile sensors, communication, computing, and AI.}
    \item \emph{Present the technologies used and any enhancements made to improve functionality or efficiency.}
    \item \emph{Include screenshots or diagrams of the app’s user interface and features.}
\end{itemize}

\section{Experimental Design and Evaluation}
\begin{itemize}
    \item \emph{\textbf{Design Rationale:} Justify the experimental design in relation to the application's objectives.}
    \item \emph{\textbf{Metrics:} Discuss the metrics used for evaluation and their relevance to the project goals.}
    \item \emph{\textbf{Results:} Present and analyze experimental results demonstrating the application’s performance against its objectives.}
\end{itemize}

\section{Conclusion}
\begin{itemize}
    \item \emph{Highlight innovations, significant breakthroughs, and summarize the overall achievements of the project.}
    \item \emph{Discuss potential future directions for further development of the application.}
\end{itemize}

\vfill
\section{Appendices}
\begin{itemize}
    \item \emph{\textbf{Individual Contributions:} Detail each team member's specific contributions to the project.}
    \item \emph{\textbf{Agile Development Process:} Summarize the agile development practices your team employed.}
    \item \emph{\textbf{Declaration of Tools and Resources:} List all tools and resources used, including any AI tools like ChatGPT or Copilot, and acknowledge any external support received.}
\end{itemize}



\newpage
\bibliography{mybib}


\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
